StarCraft Bots and Competitions

### 2015-12-11 ECGG_StarCraftCompetitions/ECGG_StarCraftCompetitions.tex
removed the * from some tables and figures, since this is a single column document
fixed a typo in the authors line, and a duplicated label in a table

\author{David~Churchill\inst{1} \and
		Mike~Preuss\inst{2}		
		Florian~Richoux\inst{3} \and
		Gabriel~Synnaeve\inst{4} \and
		Alberto~Uriarte\inst{5} \and
		Santiago~Onta\~{n}\'{o}n\inst{5} \and 
		}

@@

\begin{table}[!t]
\caption{Results of the five best bots of the AIIDE 2015 competition}
\label{tab:aiide2014}
\centering
\begin{tabular}{|c|c|c|}
\hline
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Tscmoo & 88.52\% \\
2 & ZZZKBot & 87.84\% \\
3 & Overkill & 80.69\% \\
4 & UAlbertaBot & 80.20\% \\
5 & Aiur & 73.02\% \\
\hline
\end{tabular}
\end{table}

@@

\begin{table*}[!t]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won)}
\label{tab:cig-first-round}
\centering
% bracket A
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
{\bfseries Rank} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
A1 & 0 &   40 &  UAlbertaBot & 82.5\% \\
A2 & 1 &     40 &  Skynet   &  77.5\% \\
A3 & 2 &   40 &  AIUR   &  60.0\% \\
A4 & 1 &   40 &  Nova   &  20.0\% \\
A5 & 0 &   40 &  LSAI   &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
{\bfseries Rank} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
B1 & 12 &  40 &  Xelnaga &   62.5\%\\
B2 & 3 &   40 &  BroodwarBotQ  &  57.5\%\\
B3 & 0 &   40 &  BTHAI    &  57.5\%\\
B4 & 17 &  40 &  Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &   40 &  EvoBot   &  30.0\%\\
\hline
\end{tabular}
\end{table*}

@@

\begin{figure*}[b]
	%\vspace*{-2ex}
    \centering
    \includegraphics[width=0.32\textwidth]{figures/vstable3.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable6.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable.pdf}
	%\vspace*{-4ex}
    \caption{Win percentages of CIG 2012 competition, from left
    to right: 3-player maps only, 6-player maps only, all maps.
    Read from line to column, bot in row wins given fraction of
    games against bot in column. For some bots, we find interesting
    differences, e.g. Xelnaga gets worse on 6-player maps, UAlbertaBot
    gets better. Only Xelnaga can reliably beat Skynet, but only on 
    3-player maps}
    \label{fig:cig2012-mapresults}
\end{figure*}

>>>>

\author{David~Churchill\inst{1} \and
		Mike~Preuss\inst{2} \and
		Florian~Richoux\inst{3} \and
		Gabriel~Synnaeve\inst{4} \and
		Alberto~Uriarte\inst{5} \and
		Santiago~Onta\~{n}\'{o}n\inst{5}
		}

@@

\begin{table}[!t]
\caption{Results of the five best bots of the AIIDE 2015 competition}
\label{tab:aiide2015}
\centering
\begin{tabular}{|c|c|c|}
\hline
{\bfseries Rank} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
1 & Tscmoo & 88.52\% \\
2 & ZZZKBot & 87.84\% \\
3 & Overkill & 80.69\% \\
4 & UAlbertaBot & 80.20\% \\
5 & Aiur & 73.02\% \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won)}
\label{tab:cig-first-round}
\centering
% bracket A
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
{\bfseries Rank} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
A1 & 0 &   40 &  UAlbertaBot & 82.5\% \\
A2 & 1 &     40 &  Skynet   &  77.5\% \\
A3 & 2 &   40 &  AIUR   &  60.0\% \\
A4 & 1 &   40 &  Nova   &  20.0\% \\
A5 & 0 &   40 &  LSAI   &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
{\bfseries Rank} & {\bfseries Crashes} & {\bfseries Games} & {\bfseries Bot} & {\bfseries Win \%} \\
\hline
B1 & 12 &  40 &  Xelnaga &   62.5\%\\
B2 & 3 &   40 &  BroodwarBotQ  &  57.5\%\\
B3 & 0 &   40 &  BTHAI    &  57.5\%\\
B4 & 17 &  40 &  Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &   40 &  EvoBot   &  30.0\%\\
\hline
\end{tabular}
\end{table}

@@

\begin{figure}[b]
	%\vspace*{-2ex}
    \centering
    \includegraphics[width=0.32\textwidth]{figures/vstable3.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable6.pdf}
    \includegraphics[width=0.32\textwidth]{figures/vstable.pdf}
	%\vspace*{-4ex}
    \caption{Win percentages of CIG 2012 competition, from left
    to right: 3-player maps only, 6-player maps only, all maps.
    Read from line to column, bot in row wins given fraction of
    games against bot in column. For some bots, we find interesting
    differences, e.g. Xelnaga gets worse on 6-player maps, UAlbertaBot
    gets better. Only Xelnaga can reliably beat Skynet, but only on 
    3-player maps}
    \label{fig:cig2012-mapresults}
\end{figure}
